Correlation between 16S and shotgun

### 2019-11-09 scripts/20_correlation_phylum_bw_16S_shotgun.Rmd
update

```{r}
Two %>% 
  ggplot(aes(x = shotgun_relab, y = s16S_relab, col = phylum)) +
  geom_point() +
  facet_wrap(~sampleid) +
  geom_abline(intercept = 0, slope = 1, col = 'red', linetype = 'dashed') +
  geom_vline(xintercept = 0, col= 'forestgreen', linetype = 'dashed') +
  geom_hline(yintercept = 0, col= 'forestgreen', linetype = 'dashed') +
  scale_color_manual(values = brewer.pal(n = length(ol_phylum), name = "Dark2")) +
  labs(x = 'log10(Shotgun data)',
       y = 'log10(16S data)',
       title = 'log10 transformed relative abundance comparison between shotgun and 16S data\nat phylum level') +
  ggsave('../figs/correlation/cor_between_16_and_shotgun.jpg', width = 10, height = 10, dpi = 300)

>>>>

```{r}
Two %>% 
  ggplot(aes(x = shotgun_relab, y = s16S_relab, col = phylum)) +
  geom_point(size = 3) +
  facet_wrap(~sampleid) +
  geom_abline(intercept = 0, slope = 1, col = 'pink', linetype = 'dashed') +
  geom_vline(xintercept = 0, col= 'lightgreen', linetype = 'dashed') +
  geom_hline(yintercept = 0, col= 'lightgreen', linetype = 'dashed') +
  scale_color_manual(values = brewer.pal(n = length(ol_phylum), name = "Dark2")) +
  labs(x = 'log10(Shotgun data)',
       y = 'log10(16S data)',
       title = 'log10 transformed relative abundance comparison between shotgun and 16S data\nat phylum level') +
  theme_light()+
  ggsave('../figs/correlation/cor_between_16_and_shotgun.jpg', width = 10, height = 10, dpi = 300)

### 2019-11-09 scripts/21_correlation_genus_bw_16S_shotgun.Rmd
update

```{r}
Two %>% 
  ggplot(aes(x = shotgun_relab, y = s16S_relab)) +
    geom_point() +
    facet_wrap(~sampleid) +
  geom_abline(intercept = 0, slope = 1, col = 'red', linetype = 'dashed') +
  geom_vline(xintercept = 0, col= 'forestgreen', linetype = 'dashed') +
  geom_hline(yintercept = 0, col= 'forestgreen', linetype = 'dashed') +
  labs(x = 'log10(Shotgun data)',
       y = 'log10(16S data)',
       title = 'log10 transformed relative abundance comparison between shotgun and 16S data\nat genus level') +
  theme_light()+
  ggsave('../figs/correlation/cor_between_16_and_shotgun_genus.jpg', width = 10, height = 10, dpi = 300)

# plot a single sample's plot to show the details
Two %>% 
  filter(sampleid == '275G') %>% 
  ggplot(aes(x = shotgun_relab, y = s16S_relab)) +
    geom_point() +
    geom_abline(intercept = 0, slope = 1, col = 'red', linetype = 'dashed') +
    geom_vline(xintercept = 0, col= 'forestgreen', linetype = 'dashed') +
    geom_hline(yintercept = 0, col= 'forestgreen', linetype = 'dashed') +
    labs(x = 'log10(Shotgun data)',
         y = 'log10(16S data)',
         title = 'log10(relative abundance) comparison (genus): 275G') +
    theme_light()+
    ggsave('../figs/correlation/275G_cor_between_16_and_shotgun_genus.jpg', width = 5, height = 5, dpi = 300)

@@

>>>>

```{r}
Two %>% 
  ggplot(aes(x = shotgun_relab, y = s16S_relab)) +
    geom_point() +
    facet_wrap(~sampleid) +
  geom_abline(intercept = 0, slope = 1, col = 'pink', linetype = 'dashed') +
  geom_vline(xintercept = 0, col= 'forestgreen', linetype = 'dashed') +
  geom_hline(yintercept = 0, col= 'forestgreen', linetype = 'dashed') +
  labs(x = 'log10(Shotgun data)',
       y = 'log10(16S data)',
       title = 'log10 transformed relative abundance comparison between shotgun and 16S data\nat genus level') +
  theme_light()+
  ggsave('../figs/correlation/cor_between_16_and_shotgun_genus.jpg', width = 10, height = 10, dpi = 300)

# plot a single sample's plot to show the details
Two %>% 
  filter(sampleid == '275G') %>% 
  ggplot(aes(x = shotgun_relab, y = s16S_relab)) +
    geom_point() +
    geom_abline(intercept = 0, slope = 1, col = 'pink', linetype = 'dashed') +
    geom_vline(xintercept = 0, col= 'forestgreen', linetype = 'dashed') +
    geom_hline(yintercept = 0, col= 'forestgreen', linetype = 'dashed') +
    labs(x = 'log10(Shotgun data)',
         y = 'log10(16S data)',
         title = 'log10(relative abundance) comparison (genus): 275G') +
    theme_light()+
    ggsave('../figs/correlation/275G_cor_between_16_and_shotgun_genus.jpg', width = 5, height = 5, dpi = 300)

@@

```{bash}
# create the shotgun table for the class order and family level
2
```

```{r}
compare_each_taxa_level <- function(){

}
```
